---
title       : Prediction on MPG 
subtitle    : 
author      : Pattareeya
job         : Data Scientist
framework   : html5slides      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Prediction on MPG using regression model on mtcars data set
we want to find the best regression model to determine MPG. 
Source: mtcars data set from R package
```{r,echo=FALSE}
library(datasets)
```

```{r}
data(mtcars)
```
```{r,echo=FALSE}
mtcars$cyl  <- factor(mtcars$cyl)
mtcars$vs   <- factor(mtcars$vs)
mtcars$am   <- factor(mtcars$am, labels = c("Automatic","Manual"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
pairs(mtcars, panel = panel.smooth, col = 3 )
```

---

## Create Best Fit Model 

```{r,results='hide'}
model1 <- lm(mpg ~ ., mtcars) #initial model
best_model <- step(model1, direction = "both") #best fit model
```

```{r,echo=FALSE}
summary(best_model)
```


It shows that *cyl*, *hp*, *wt* and *am* are the predictors on our model

---

## Determine how fit the model is

We use R-squared to determine how fit the regression model to the data.

```{r}
summary(best_model)$r.squared
```


It shows that the R-squared is high enough for us to use this as the prediction model.

---

## Residulas, Normal Q-Q, Scalse-Location & Leverage

```{r,echo=FALSE}
par(mfrow=c(2,2))
plot(best_model)
title("Figure 2: Residuals, Normal Q-Q, Scale-Location, & Leverage", line = -1,  outer = TRUE)
```


From these plots, we can say that our model is really really good model.

---

## Conclusion

We want to predict the MPG and select the most influent predictors from linear regression model. As the result, those influent predictors are
- Cylinder: 4, 6, 8
- Transmission Type: Automatic, Manual
- Horse Power: 52-335
- Weight( lb/1000): 1-5
